### 2012-02-02 paper.tex
Added a bit of content to the results section

\section{Results}
During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce. In agreement with litterature\cite{Singh2010} (FLERE REFS), we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle. In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations. This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals (REF TIL FRENKEN).

@@

If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. 
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

@@

>>>>

\section{Results}
During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce. In agreement with litterature\cite{Singh2010,Hendriksen2005}, we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle. In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations. This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals\cite{Hendriksen2005}.

@@

Most measurements where done at 1\,bar, however no clear pressure dependence is seen within a pressure range of at least 0.1\,bar to 1\,bar, the oscillations neither change their period nor qualitative behaviour significantly. Similarly, only a rather weak dependence on the CO pressure is seen. Oscillations is barely visible in the mass-spectrometry from a CO-concentration of $\sim0.025$ and is then seen up to concentrations of $\sim0.175$. A tendendcy towards slower oscillations for higher CO-concentrations is seen, but the effect is not very large.

If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. Analysing the on/off ratio of the oscillations doing the full period of time shows that the ratio is unaffected across the entire period of the measurement, the oscillations are qualititively almost identical even though the period is changed by a factor of 10 doing the measurement.
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

@@

The exact mechanisum of CO oxidation on Pt is still under debate, but concesus seems to be, that the most active phase is a skin of Pt-oxide on top of metallic Pt. ..... .... ... ...

The phenomenon of increasing oscillation period over time is completely consistent across all measured samples, and it must originate from a real physical phenomen. A possible explanation of the phenomenon could be sintering or roughening of the clusters.
